---
title: "Weed analysis"
author: "Craig Simpkins"
format: pdf
editor: visual
---

```{r}
#| label: load-data
#| include: false

library(tidyverse)
library(data.table)
library(wesanderson)
library(ggpubr)

distinct <- data.table::fread("weed_impact_distinct_wide.csv")
ff <- data.table::fread("weed_sensitivity_ff_wide.csv")
```

```{r}
#| label: lengthen dataframes
#| include: false

distinct_long <- distinct %>% 
  pivot_longer(
    cols = BA_tawa:abundance_kanuka,
    names_to = c(".value", "species"),
    names_pattern = "(.*)_(.*)"
  )

ff_long <- ff %>% 
  pivot_longer(
    cols = BA_tawa:abundance_kanuka,
    names_to = c(".value", "species"),
    names_pattern = "(.*)_(.*)"
  )

distinct_long <- data.table(distinct_long)
ff_long <- data.table(ff_long)
```

```{r}
#| label: summarise data
#| include: false

## Note we remove BA here as it is always 0 due to critical code being
## commented out in the Netlogo model itself

distinct_summary <- distinct_long[, 
                                  list(mean_age = mean(age),
                                  mean_dbh = mean(dbh),
                                  mean_hgt = mean(hgt),
                                  mean_abundance = mean(abundance)),
                                  by = list(ground_weeds, step, species)
                                  ]

ff_summary <- ff_long[, 
                      list(mean_age = mean(age),
                      mean_dbh = mean(dbh),
                      mean_hgt = mean(hgt),
                      mean_abundance = mean(abundance)),
                      by = list(trad_init_cover,
                                smother_f,
                                trad_spread_local,
                                trad_spread_long,
                                trad_growth,
                                step, 
                                species)
                      ]
```

## Impact of weeds

Ran model for 1000 steps for 15 repeats with ground weeds on and off. Weed parameters were randomly selected based on initial settings and only testing the clustered scenario. The parameter values were:

-   trad-init-cover = 0.150
-   trad-spread-local = 0.20
-   trad-spread-long = 0.025
-   trad-growth = 1.0
-   smother-f = 0.20

```{r}
#| label: plot distinct changes
#| fig-cap: Composition measures for each species taken at 1000 time steps (years) with and with out ground weed cover, presented as the mean of the 15 model repeats.
#| echo: false

distinct_summary$species <- factor(distinct_summary$species,
                                   levels = c("tawa",
                                              "pigeon",
                                              "pukatea",
                                              "kawakawa",
                                              "mahoe",
                                              "rimu",
                                              "ponga",
                                              "kanuka"))



abundance <- ggplot(distinct_summary[step == 100], 
                    aes(fill=ground_weeds, x = species, y = mean_abundance)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = c("#46ACC8", "#E58601")) + 
  theme_classic() +
  xlab("Species") +
  ylab("Mean abundance")

age <- ggplot(distinct_summary[step == 100], 
              aes(fill=ground_weeds, x = species, y = mean_age)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = c("#46ACC8", "#E58601")) + 
  theme_classic() +
  xlab("Species") +
  ylab("Mean age")

dbh <- ggplot(distinct_summary[step == 100], 
              aes(fill=ground_weeds, x = species, y = mean_dbh)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = c("#46ACC8", "#E58601")) + 
  theme_classic() +
  xlab("Species") +
  ylab("Mean DBH")

hgt <- ggplot(distinct_summary[step == 100], 
              aes(fill=ground_weeds, x = species, y = mean_hgt)) + 
  geom_bar(position="dodge", stat="identity") +
  scale_fill_manual(values = c("#46ACC8", "#E58601")) + 
  theme_classic() +
  xlab("Species") +
  ylab("Mean height")


ggarrange(abundance + rremove("x.text") + rremove("xlab"), 
          dbh + rremove("x.text") + rremove("xlab"), 
          hgt + theme(axis.text.x = element_text(angle = 20)), 
          age + theme(axis.text.x = element_text(angle = 20)), 
          common.legend = TRUE,
          ncol = 2, nrow = 2)
```

## Impact of weed parameters (i.e. sensitivity)

Sensitivity analysis model runs were run for 1000 steps, repeated six times (due to time constraints) for every parameter value combination. Note that parameter values were altered by 100% above and below baseline levels, e.g., if baseline was 0.5 runs were conducted at 0 and 1. This high degree of change was done to allow for analysis of impact of extreme changes in addition to sensitivity.

```{r}
#| label: subset data for sensitivity
#| include: false

## Man this is dirty sure there is a better way
## Baseline
ff_baseline <- ff_summary[trad_init_cover == 0.5 &
                            smother_f == 0.5 &
                            trad_spread_local == 0.5 &
                            trad_spread_long == 0.5 &
                            trad_growth == 1.25]

## Initial cover
ff_init_cov_up <- ff_summary[trad_init_cover == 1 &
                               smother_f == 0.5 &
                               trad_spread_local == 0.5 &
                               trad_spread_long == 0.5 &
                               trad_growth == 1.25]

ff_init_cov_down <- ff_summary[trad_init_cover == 0 &
                                 smother_f == 0.5 &
                                 trad_spread_local == 0.5 &
                                 trad_spread_long == 0.5 &
                                 trad_growth == 1.25]

## Smother f
ff_smother_up <- ff_summary[trad_init_cover == 0.5 &
                              smother_f == 1 &
                              trad_spread_local == 0.5 &
                              trad_spread_long == 0.5 &
                              trad_growth == 1.25]

ff_smother_down <- ff_summary[trad_init_cover == 0.5 &
                                smother_f == 0 &
                                trad_spread_local == 0.5 &
                                trad_spread_long == 0.5 &
                                trad_growth == 1.25]

## Spread local
ff_spread_local_up <- ff_summary[trad_init_cover == 0.5 &
                                   smother_f == 0.5 &
                                   trad_spread_local == 1 &
                                   trad_spread_long == 0.5 &
                                   trad_growth == 1.25]

ff_spread_local_down <- ff_summary[trad_init_cover == 0.5 &
                                     smother_f == 0.5 &
                                     trad_spread_local == 0 &
                                     trad_spread_long == 0.5 &
                                     trad_growth == 1.25]

## Spread long
ff_spread_long_up <- ff_summary[trad_init_cover == 0.5 &
                                  smother_f == 0.5 &
                                  trad_spread_local == 0.5 &
                                  trad_spread_long == 1 &
                                  trad_growth == 1.25]

ff_spread_long_down <- ff_summary[trad_init_cover == 0.5 &
                                    smother_f == 0.5 &
                                    trad_spread_local == 0.5 &
                                    trad_spread_long == 0 &
                                    trad_growth == 1.25]

## Growth
ff_growth_up <- ff_summary[trad_init_cover == 0.5 &
                             smother_f == 0.5 &
                             trad_spread_local == 0.5 &
                             trad_spread_long == 0.5 &
                             trad_growth == 2.5]

ff_growth_down <- ff_summary[trad_init_cover == 0.5 &
                               smother_f == 0.5 &
                               trad_spread_local == 0.5 &
                               trad_spread_long == 0.5 &
                               trad_growth == 0]
```

```{r}
#| label: create sensitivity calculation function
#| include: false

calc_hamby <- function(y, x, base_y, base_x){
  
  delta_y <- abs(y - base_y)
  delta_x <- abs(x - base_x)
  
  sens <- (delta_y/base_y)/(delta_x/base_x)
  
  sens[is.nan(sens)] <- 0
  sens[is.infinite(sens)] <- 0
  return(sens)
}
```

```{r}
#| label: calculate sensitivity
#| include: false

## Baseline just to allow join
ff_baseline$ab_hamby <- calc_hamby(ff_baseline$mean_abundance,
                                ff_baseline$trad_init_cover,
                                ff_baseline$mean_abundance,
                                ff_baseline$trad_init_cover)

ff_baseline$dbh_hamby <- calc_hamby(ff_baseline$mean_dbh,
                                ff_baseline$trad_init_cover,
                                ff_baseline$mean_dbh,
                                ff_baseline$trad_init_cover)

ff_baseline$hgt_hamby <- calc_hamby(ff_baseline$mean_hgt,
                                ff_baseline$trad_init_cover,
                                ff_baseline$mean_hgt,
                                ff_baseline$trad_init_cover)

ff_baseline$age_hamby <- calc_hamby(ff_baseline$mean_age,
                                ff_baseline$trad_init_cover,
                                ff_baseline$mean_age,
                                ff_baseline$trad_init_cover)

## Initial cover
## Increase
ff_init_cov_up$ab_hamby <- calc_hamby(ff_init_cov_up$mean_abundance,
                                   ff_init_cov_up$trad_init_cover,
                                   ff_baseline$mean_abundance,
                                   ff_baseline$trad_init_cover)

ff_init_cov_up$dbh_hamby <- calc_hamby(ff_init_cov_up$mean_dbh,
                                   ff_init_cov_up$trad_init_cover,
                                   ff_baseline$mean_dbh,
                                   ff_baseline$trad_init_cover)

ff_init_cov_up$hgt_hamby <- calc_hamby(ff_init_cov_up$mean_hgt,
                                   ff_init_cov_up$trad_init_cover,
                                   ff_baseline$mean_hgt,
                                   ff_baseline$trad_init_cover)

ff_init_cov_up$age_hamby <- calc_hamby(ff_init_cov_up$mean_age,
                                   ff_init_cov_up$trad_init_cover,
                                   ff_baseline$mean_age,
                                   ff_baseline$trad_init_cover)

## Decrease
ff_init_cov_down$ab_hamby <- calc_hamby(ff_init_cov_down$mean_abundance,
                                     ff_init_cov_down$trad_init_cover,
                                     ff_baseline$mean_abundance,
                                     ff_baseline$trad_init_cover)

ff_init_cov_down$dbh_hamby <- calc_hamby(ff_init_cov_down$mean_dbh,
                                     ff_init_cov_down$trad_init_cover,
                                     ff_baseline$mean_dbh,
                                     ff_baseline$trad_init_cover)

ff_init_cov_down$hgt_hamby <- calc_hamby(ff_init_cov_down$mean_hgt,
                                     ff_init_cov_down$trad_init_cover,
                                     ff_baseline$mean_hgt,
                                     ff_baseline$trad_init_cover)

ff_init_cov_down$age_hamby <- calc_hamby(ff_init_cov_down$mean_age,
                                     ff_init_cov_down$trad_init_cover,
                                     ff_baseline$mean_age,
                                     ff_baseline$trad_init_cover)

## Smother f
## Increase
ff_smother_up$ab_hamby <- calc_hamby(ff_smother_up$mean_abundance,
                                  ff_smother_up$smother_f,
                                  ff_baseline$mean_abundance,
                                  ff_baseline$trad_init_cover)

ff_smother_up$dbh_hamby <- calc_hamby(ff_smother_up$mean_dbh,
                                  ff_smother_up$smother_f,
                                  ff_baseline$mean_dbh,
                                  ff_baseline$trad_init_cover)

ff_smother_up$hgt_hamby <- calc_hamby(ff_smother_up$mean_hgt,
                                  ff_smother_up$smother_f,
                                  ff_baseline$mean_hgt,
                                  ff_baseline$trad_init_cover)

ff_smother_up$age_hamby <- calc_hamby(ff_smother_up$mean_age,
                                  ff_smother_up$smother_f,
                                  ff_baseline$mean_age,
                                  ff_baseline$trad_init_cover)

## Decrease
ff_smother_down$ab_hamby <- calc_hamby(ff_smother_down$mean_abundance,
                                    ff_smother_down$smother_f,
                                    ff_baseline$mean_abundance,
                                    ff_baseline$trad_init_cover)

ff_smother_down$dbh_hamby <- calc_hamby(ff_smother_down$mean_dbh,
                                    ff_smother_down$smother_f,
                                    ff_baseline$mean_dbh,
                                    ff_baseline$trad_init_cover)

ff_smother_down$hgt_hamby <- calc_hamby(ff_smother_down$mean_hgt,
                                    ff_smother_down$smother_f,
                                    ff_baseline$mean_hgt,
                                    ff_baseline$trad_init_cover)

ff_smother_down$age_hamby <- calc_hamby(ff_smother_down$mean_age,
                                    ff_smother_down$smother_f,
                                    ff_baseline$mean_age,
                                    ff_baseline$trad_init_cover)

## Spread local
## Increase
ff_spread_local_up$ab_hamby <- calc_hamby(ff_spread_local_up$mean_abundance,
                                       ff_spread_local_up$trad_spread_local,
                                       ff_baseline$mean_abundance,
                                       ff_baseline$trad_init_cover)

ff_spread_local_up$dbh_hamby <- calc_hamby(ff_spread_local_up$mean_dbh,
                                       ff_spread_local_up$trad_spread_local,
                                       ff_baseline$mean_dbh,
                                       ff_baseline$trad_init_cover)

ff_spread_local_up$hgt_hamby <- calc_hamby(ff_spread_local_up$mean_hgt,
                                       ff_spread_local_up$trad_spread_local,
                                       ff_baseline$mean_hgt,
                                       ff_baseline$trad_init_cover)

ff_spread_local_up$age_hamby <- calc_hamby(ff_spread_local_up$mean_age,
                                       ff_spread_local_up$trad_spread_local,
                                       ff_baseline$mean_age,
                                       ff_baseline$trad_init_cover)

## Decrease
ff_spread_local_down$ab_hamby <- calc_hamby(ff_spread_local_down$mean_abundance,
                                         ff_spread_local_down$trad_spread_local,
                                         ff_baseline$mean_abundance,
                                         ff_baseline$trad_init_cover)

ff_spread_local_down$dbh_hamby <- calc_hamby(ff_spread_local_down$mean_dbh,
                                         ff_spread_local_down$trad_spread_local,
                                         ff_baseline$mean_dbh,
                                         ff_baseline$trad_init_cover)

ff_spread_local_down$hgt_hamby <- calc_hamby(ff_spread_local_down$mean_hgt,
                                         ff_spread_local_down$trad_spread_local,
                                         ff_baseline$mean_hgt,
                                         ff_baseline$trad_init_cover)

ff_spread_local_down$age_hamby <- calc_hamby(ff_spread_local_down$mean_age,
                                         ff_spread_local_down$trad_spread_local,
                                         ff_baseline$mean_age,
                                         ff_baseline$trad_init_cover)

## Spread long
## Increase
ff_spread_long_up$ab_hamby <- calc_hamby(ff_spread_long_up$mean_abundance,
                                      ff_spread_long_up$trad_spread_long,
                                      ff_baseline$mean_abundance,
                                      ff_baseline$trad_init_cover)

ff_spread_long_up$dbh_hamby <- calc_hamby(ff_spread_long_up$mean_dbh,
                                      ff_spread_long_up$trad_spread_long,
                                      ff_baseline$mean_dbh,
                                      ff_baseline$trad_init_cover)

ff_spread_long_up$hgt_hamby <- calc_hamby(ff_spread_long_up$mean_hgt,
                                      ff_spread_long_up$trad_spread_long,
                                      ff_baseline$mean_hgt,
                                      ff_baseline$trad_init_cover)

ff_spread_long_up$age_hamby <- calc_hamby(ff_spread_long_up$mean_age,
                                      ff_spread_long_up$trad_spread_long,
                                      ff_baseline$mean_age,
                                      ff_baseline$trad_init_cover)

## Decrease
ff_spread_long_down$ab_hamby <- calc_hamby(ff_spread_long_down$mean_abundance,
                                        ff_spread_long_down$trad_spread_long,
                                        ff_baseline$mean_abundance,
                                        ff_baseline$trad_init_cover)

ff_spread_long_down$dbh_hamby <- calc_hamby(ff_spread_long_down$mean_dbh,
                                        ff_spread_long_down$trad_spread_long,
                                        ff_baseline$mean_dbh,
                                        ff_baseline$trad_init_cover)

ff_spread_long_down$hgt_hamby <- calc_hamby(ff_spread_long_down$mean_hgt,
                                        ff_spread_long_down$trad_spread_long,
                                        ff_baseline$mean_hgt,
                                        ff_baseline$trad_init_cover)

ff_spread_long_down$age_hamby <- calc_hamby(ff_spread_long_down$mean_age,
                                        ff_spread_long_down$trad_spread_long,
                                        ff_baseline$mean_age,
                                        ff_baseline$trad_init_cover)

## Growth
## Increase
ff_growth_up$ab_hamby <- calc_hamby(ff_growth_up$mean_abundance,
                                 ff_growth_up$trad_growth,
                                 ff_baseline$mean_abundance,
                                 ff_baseline$trad_init_cover)

ff_growth_up$dbh_hamby <- calc_hamby(ff_growth_up$mean_dbh,
                                 ff_growth_up$trad_growth,
                                 ff_baseline$mean_dbh,
                                 ff_baseline$trad_init_cover)

ff_growth_up$hgt_hamby <- calc_hamby(ff_growth_up$mean_hgt,
                                 ff_growth_up$trad_growth,
                                 ff_baseline$mean_hgt,
                                 ff_baseline$trad_init_cover)

ff_growth_up$age_hamby <- calc_hamby(ff_growth_up$mean_age,
                                 ff_growth_up$trad_growth,
                                 ff_baseline$mean_age,
                                 ff_baseline$trad_init_cover)

## Decrease
ff_growth_down$ab_hamby <- calc_hamby(ff_growth_down$mean_abundance,
                                   ff_growth_down$trad_growth,
                                   ff_baseline$mean_abundance,
                                   ff_baseline$trad_init_cover)

ff_growth_down$dbh_hamby <- calc_hamby(ff_growth_down$mean_dbh,
                                   ff_growth_down$trad_growth,
                                   ff_baseline$mean_dbh,
                                   ff_baseline$trad_init_cover)

ff_growth_down$hgt_hamby <- calc_hamby(ff_growth_down$mean_hgt,
                                   ff_growth_down$trad_growth,
                                   ff_baseline$mean_hgt,
                                   ff_baseline$trad_init_cover)

ff_growth_down$age_hamby <- calc_hamby(ff_growth_down$mean_age,
                                   ff_growth_down$trad_growth,
                                   ff_baseline$mean_age,
                                   ff_baseline$trad_init_cover)


## Combine back together
sensitivity_DT <- rbindlist(list(ff_baseline,
                                 ff_init_cov_up,
                                 ff_init_cov_down,
                                 ff_smother_up,
                                 ff_smother_down,
                                 ff_spread_local_up,
                                 ff_spread_local_down,
                                 ff_spread_long_up,
                                 ff_spread_long_down,
                                 ff_growth_up,
                                 ff_growth_down))

```

```{r}
#| label: format sensitivity
#| echo: false

var_name_list <- list("baseline",
                      "cover", "cover",
                      "smother", "smother",
                      "spread_local", "spread_local",
                      "LDD", "LDD",
                      "growth", "growth")

change_dir_list <- c("none",rep(list("increase","decrease"), 5))

sensitivity_DT$focus_parameter <- unlist(rep(var_name_list, each=80))
sensitivity_DT$direction <- unlist(rep(change_dir_list, each=80))

sensitivity_DT[ab_hamby > 3]$ab_hamby <- 3
sensitivity_DT[dbh_hamby > 3]$dbh_hamby <- 3
sensitivity_DT[hgt_hamby > 3]$hgt_hamby <- 3
sensitivity_DT[age_hamby > 3]$age_hamby <- 3
```

```{r}
#| label: plot sensitivities
#| echo: false

plot_data <- sensitivity_DT[focus_parameter != "baseline" &
                              step == 1000]

ab <- ggplot(plot_data, aes(x = focus_parameter, 
                            y = ab_hamby,
                            fill = direction)) +
  geom_boxplot(outlier.shape = NA) +
  geom_dotplot(binaxis='y', 
               stackdir='center',
               position=position_dodge(0.8),
               dotsize = 0.5,
               binwidth = 1/11,
               fill = "black",
               aes(colour = direction)) +
  geom_hline(yintercept = 1,
             linetype="dashed", 
             color = "darkgray") +
  theme_classic() +
  ylab("Hamby sensitivity index") +
  xlab("Adjusted parameter") + 
  #labs(fill = "Direction of \nchange") + 
  scale_fill_manual(values = c("#46ACC8", "#E58601")) +
  scale_color_manual(values = c("black", "black")) + 
  guides(color = "none")

dbh <- ggplot(plot_data, aes(x = focus_parameter, 
                             y = dbh_hamby,
                             fill = direction)) +
  geom_boxplot(outlier.shape = NA) +
  geom_dotplot(binaxis='y', 
               stackdir='center',
               position=position_dodge(0.8),
               dotsize = 0.5,
               binwidth = 1/30,
               fill = "black",
               aes(colour = direction)) +
  geom_hline(yintercept = 1,
             linetype="dashed", 
             color = "darkgray") +
  theme_classic() +
  ylab("Hamby sensitivity index") +
  xlab("Adjusted parameter") + 
  #labs(fill = "Direction of \nchange") + 
  scale_fill_manual(values = c("#46ACC8", "#E58601")) +
  scale_color_manual(values = c("black", "black")) + 
  guides(color = "none")

hgt <- ggplot(plot_data, aes(x = focus_parameter, 
                             y = hgt_hamby,
                             fill = direction)) +
  geom_boxplot(outlier.shape = NA) +
  geom_dotplot(binaxis='y', 
               stackdir='center',
               position=position_dodge(0.8),
               dotsize = 0.5,
               binwidth = 1/30,
               fill = "black",
               aes(colour = direction)) +
  geom_hline(yintercept = 1,
             linetype="dashed", 
             color = "darkgray") +
  theme_classic() +
  ylab("Hamby sensitivity index") +
  xlab("Adjusted parameter") + 
  #labs(fill = "Direction of \nchange") + 
  scale_fill_manual(values = c("#46ACC8", "#E58601")) +
  scale_color_manual(values = c("black", "black")) + 
  guides(color = "none")

age <- ggplot(plot_data, aes(x = focus_parameter, 
                             y = age_hamby,
                             fill = direction)) +
  geom_boxplot(outlier.shape = NA) +
  geom_dotplot(binaxis='y', 
               stackdir='center',
               position=position_dodge(0.8),
               dotsize = 0.5,
               binwidth = 1/30,
               fill = "black",
               aes(colour = direction)) +
  geom_hline(yintercept = 1,
             linetype="dashed", 
             color = "darkgray") +
  theme_classic() +
  ylab("Hamby sensitivity index") +
  xlab("Adjusted parameter") + 
  #labs(fill = "Direction of \nchange") + 
  scale_fill_manual(values = c("#46ACC8", "#E58601")) +
  scale_color_manual(values = c("black", "black")) + 
  guides(color = "none")
```

::: panel-tabset
## Abundance

```{r}
#| label: plot abundance
#| echo: false

ab
```

## DBH

```{r}
#| label: plot dbh
#| echo: false

dbh
```

## Height

```{r}
#| label: plot hgt
#| echo: false

hgt
```

## Age

```{r}
#| label: plot age
#| echo: false

age
```
:::

## Resilience to extreme parameter values

Selected the parameter settings which had the largest percentage change compared to the no ground weed runs.

```{r}
#| label: analyse extremes
#| echo: false

prop_diff <- function(alter, base){
  return((abs(base - alter)/base) * 100)
}

extremes_sum <- ff_summary[step == 1000,
                           list(mean_abundance,
                                mean_dbh,
                                mean_hgt,
                                mean_age),
                           list(trad_init_cover,
                                smother_f,
                                trad_spread_local,
                                trad_spread_long,
                                trad_growth,
                                species)]

no_weeds <- distinct_summary[step == 1000 & ground_weeds == FALSE,
                             list(base_abundance = mean_abundance,
                                  base_dbh = mean_dbh,
                                  base_hgt = mean_hgt,
                                  base_age = mean_age),
                             list(species)]

extremes_sum <- merge.data.table(extremes_sum, no_weeds,
                                 by.x = "species", by.y = "species")

extremes_sum <- extremes_sum[, 
                             list(trad_init_cover,
                                  smother_f,
                                  trad_spread_local,
                                  trad_spread_long,
                                  trad_growth,
                                  species,
                                  abun_diff = mean_abundance - base_abundance,
                                  dbh_diff = mean_dbh - base_dbh,
                                  hgt_diff = mean_hgt - base_hgt,
                                  age_diff = mean_age - base_age,
                                  abun_per = prop_diff(mean_abundance, 
                                                       base_abundance),
                                  dbh_per = prop_diff(mean_dbh,
                                                      base_dbh),
                                  hgt_per = prop_diff(mean_hgt,
                                                      base_hgt),
                                  age_per = prop_diff(mean_age,
                                                      base_age))]


ex_abun <- extremes_sum %>% 
  group_by(species) %>% 
  slice_max(abun_per, n = 1, with_ties = FALSE) %>% 
  select(trad_init_cover,
         smother_f,
         trad_spread_local,
         trad_spread_long,
         trad_growth,
         species,
         abun_diff,
         abun_per)

ex_dbh <- extremes_sum %>% 
  group_by(species) %>% 
  slice_max(dbh_per, n = 1, with_ties = FALSE) %>% 
  select(trad_init_cover,
         smother_f,
         trad_spread_local,
         trad_spread_long,
         trad_growth,
         species,
         dbh_diff,
         dbh_per)

ex_hgt <- extremes_sum %>% 
  group_by(species) %>% 
  slice_max(hgt_per, n = 1, with_ties = FALSE) %>% 
  select(trad_init_cover,
         smother_f,
         trad_spread_local,
         trad_spread_long,
         trad_growth,
         species,
         hgt_diff,
         hgt_per)

ex_age <- extremes_sum %>% 
  group_by(species) %>% 
  slice_max(age_per, n = 1, with_ties = FALSE) %>% 
  select(trad_init_cover,
         smother_f,
         trad_spread_local,
         trad_spread_long,
         trad_growth,
         species,
         age_diff,
         age_per)
```

::: panel-tabset
## Abundance

```{r}
#| label: abundance extremes table
#| echo: false

library(knitr)
kable(ex_abun)
```

## DBH

```{r}
#| label: dbh extremes table
#| echo: false

kable(ex_dbh)
```

## Height

```{r}
#| label: height extremes table
#| echo: false

kable(ex_hgt)
```

## Age

```{r}
#| label: age extremes table
#| echo: false

kable(ex_age)
```
:::
